`r glue::glue('Compare aggregated and non-aggregated reference: {params$library_id}')`

### 2025-07-07 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/reference-aggregation.Rmd
wording about valdation groupings and stromal

## Comparison with consensus cell type annotations
### Heatmap: Aggregated vs. consensus annotations

This heatmap compares annotations between `SingleR` inference using the aggregated reference and consensus cell types.
The broader validation grouping for consensus cell types is used to keep the plot manageable.

@@

This heatmap compares annotations between `SingleR` inference using the non-aggregated reference and consensus cell types.
The broader validation grouping for consensus cell types is used to keep the plot manageable.

@@

Before plotting cell type labels were harmonized to the extent possible to that `NBAtlas` labels matched the corresponding consensus cell type labels (e.g., `Fibroblast` -> `fibroblast` or `Endothelial` -> `endothelial cell`).
Cell types that were not literally just spelling variants were left alone.

>>>>

## Comparison with consensus cell type annotations

In this section, we compare aggregated & non-aggregated annotations to the consensus cell type labels.
In these comparisons, we consider the broader validation groupings for consensus cell types in order to keep plots manageable and more easily interpreted.

### Heatmap: Aggregated vs. consensus annotations

This heatmap compares annotations between `SingleR` inference using the aggregated reference and consensus cell types.

@@

This heatmap compares annotations between `SingleR` inference using the non-aggregated reference and consensus cell types.

@@

Before plotting cell type labels were harmonized to the extent possible to that `NBAtlas` labels matched the corresponding consensus cell type labels (e.g., `Fibroblast` -> `fibroblast` or `Endothelial` -> `endothelial cell`).
Cell types that were not literally just spelling variants were left alone; note that `stromal` cell types between references were also not harmonized since this group doesn't always have a clear definition.
